### 2017-11-30 latex/draft.tex
MOre Spell check

So from the mentioned algorithm it is quite evident that, the remainder (\texttt{•}{r}) of the modulus operation is being treated as one of the input of subsequent recursive function call, and also happens to be the \textbf{smallest} of the two parameters.

\section{Purpose}
The main purpose of this paper is to show whether this number \texttt{r} is unique for our \textit{gcd} algorithm purpose, or there exist another number that can also be substituted for this number?

@@

\section{Conclusion}
From the table 4 contents it is clear that by using the \texttt{min(r,s)} is advantageous and bring down the number of recursion. And also it is proved that we have a substitute for \texttt{r} in the context of modulus arithmetic and which can be used within the intermediate steps of the algorithm to find gcd of two numbers. The order of optimization is still under investigation and could be significant when we integers with very very long digits may be in the order of thousands!

>>>>

So from the mentioned algorithm it is quite evident that, the remainder (\texttt{r}) of the modulus operation is being treated as one of the input of subsequent recursive function call, and also happens to be the \textbf{smallest} of the two parameters.

\section{Purpose}
The main purpose of this paper is to show whether this number \texttt{r} is unique for our \textit{gcd} algorithm purpose, or there exists another number that can also be substituted for this number?

@@

\section{Conclusion}
From the table 4 contents it is clear that by using the \texttt{min(r,s)} is advantageous and bring down the number of recursion. And also it is proved that we have a substitute for \texttt{r} in the context of modulus arithmetic and which can be used within the intermediate steps of the algorithm to find gcd of two numbers. The order of optimization is still under investigation and could be significant when we integers with very very long digits may be in the order of thousands! Having
